Water Management

### 2020-02-11 Paper/paper.tex
update graph
add new pages after logical sections to keep the images together. We might be able to remove this hack again after we finished the texts
rainfall with higher standard deviation

\usepackage{graphicx} % for figures

@@

	\begin{figure}[ht]
		\includegraphics[width=1\textwidth]{figures/steadyStateMonteCarlo.eps}
		\caption{Steady State Probability}
		\label{fig:steadyStateMonteCarlo}
	\end{figure}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	When altering the discount factor $\beta$ in a range from 0 to 1, the optimal irrigation policy changes.
	Looking at small water levels within the reservoir the optimal irrigation amount does not change much depending on the discount factor.
	A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. 
	This leads to a increasing gap between irrigation amounts over $\beta$ with increasing water level since conserving water does not increase the usage as much.
	\begin{figure}[ht]
		\includegraphics[width=1\textwidth]{figures/optimum-policy-over-beta.eps}
		\caption{Optimal irrigation policy as a function of the discount factor $\beta$}
		\label{fig:optimal-irrigation-beta}
	\end{figure}
	\subsection{Changed Volatility of Rainfalls}

	\printbibliography

>>>>

\usepackage{graphicx} % for figures
\usepackage{subcaption}

@@

	\begin{figure}[ht]
		\includegraphics[width=1\textwidth]{figures/steadyStateMonteCarlo.eps}
		\caption{Steady State Probability}
		\label{fig:steadyStateMonteCarlo}
	\end{figure}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	When altering the discount factor $\beta$ in a range from 0 to 1, the optimal irrigation policy changes.
	Looking at small water levels within the reservoir the optimal irrigation amount does not change much depending on the discount factor.
	A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. 
	This leads to a increasing gap between irrigation amounts over $\beta$ with increasing water level since conserving water does not increase the usage as much.
	One can say that a high $\beta$ prefers a long-term policy while a smaller $\beta$ leads to a rather short-term policy.
	\begin{figure}[ht]
		\includegraphics[width=1\textwidth]{figures/optimum-policy-over-beta.eps}
		\caption{Optimal irrigation policy as a function of the discount factor $\beta$}
		\label{fig:optimal-irrigation-beta}
	\end{figure}
	\newpage
	\subsection{Changed Volatility of Rainfalls}
	A more volatile rainfall means a rainfall having a higher standard deviation.
	Since we want to compare two rainfall distributions of the same mean, the median of the distribution has to be changed.
	Using a $\sigma^2=2$ includes a mean of $\mu=-1.5$ in order for the mean to stay the same. 
	(See \ref{eq:rainfall} for reference) 
	\begin{equation}
		mean = exp(\mu+\frac{\sigma^2}{2}) \label{eq:rainfall}
	\end{equation} 
	Both distributions are visualized in \ref{fig:rain-distributions}.
	\begin{figure}
		\begin{subfigure}{0.5\textwidth}
			\centering
			\includegraphics[width=1\textwidth]{figures/rainfall-default.eps}
			\caption{$\mu=0, \sigma=1$}
			\label{fig:rainfall-default}
		\end{subfigure}%
		\begin{subfigure}{.5\textwidth}
			\centering
			\includegraphics[width=1\textwidth]{figures/rainfall-more-volatile.eps}
			\caption{$\mu=-1.5, \sigma=2$}
			\label{fig:rainfall-changed}
		\end{subfigure}
		\caption{Different Rain Distributions}
		\label{fig:rain-distributions}
	\end{figure}
	\newpage
	\printbibliography
